Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-28 writeup/gz_hubble_data.tex
Single figure for all COSMOS comparisons

\begin{itemize}
    \item \citet[ZEST;][]{sca07} (COSMOS)
    \item Tasca (COSMOS)
    \item Cassata (COSMOS)
    \item Zajmoski (COSMOS)
    \item \sout{GEMS morphologies} \citep{hau07}
    \item \sout{AEGIS morphologies} \citep{lot08}
    \item \sout{GOODS N/S morphologies} \citep{bun05}
\end{itemize}

@@

@@

>>>>

\begin{itemize}
    \item \citet[ZEST;][]{sca07} (COSMOS)
    \item \sout{Tasca (COSMOS)} \citep{tas11}
    \item \sout{Cassata (COSMOS)} \citep{cas07}
    \item \sout{Zamojski (COSMOS)} - \citet{zam07} measure parameters, but no assignation to discrete categories
    \item \sout{GEMS morphologies} \citep{hau07}
    \item \sout{AEGIS morphologies} \citep{lot08}
    \item \sout{GOODS N/S morphologies} \citep{bun05}
\end{itemize}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.50\textwidth]{figures/cosmos_comparisons.png}
\caption{Distributions of morphological parameters for COSMOS galaxies matched in GZH and various machine-learning catalogs. The left column of plots shows the fraction of overall galaxies in discrete morphology \citep{cas07,tas11,sca07} as a function of \pbest in GZH. The right column shows the same split into morphological categories as a function of \podd.}
\label{fig:cosmos_comparisons}
\end{center}
\end{figure}

@@

\citet{sca07} provide a more extensive classification of the COSMOS galaxies using a non-parametric analysis based on $A$, $C$, $G$, $M_{20}$, ellipticity ($\epsilon$), and $n$ and use a principal component analysis to assign galaxies with $m_\mathrm{I,AB}$ to discrete morphological categories.
